Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-09-18 write_up/mixfishsim_ecolmod.tex
Nothing

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on population targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries.
\\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true underlying populations. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.
\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\

>>>>

%%
To understand how data resolution impacts inference on mixed fisheries
interactions we developed a highly resolved spatiotemporal discrete-event
simulation model incorporating: i) delay-difference population dynamics, ii)
population movement using Gaussian Random Fields to simulate patchy,
heterogeneously distributed populations, and iii) fishery dynamics for multiple
fleet characteristics based on population targeting under an explore-exploit
strategy. This is implemented via a mix of correlated random walk movement (for
exploration) and learned behaviour (for exploitation) phases of the fisheries. \\ 
%%
Fifty years of sub-daily fishing activity was simulated and used to draw
inference on the underlying community structures. We compared inferences based
on: commercial catch, a simulated fixed-site sampling survey design and the
true underlying populations. We i) establish the potential limitations of
fishery-dependent data in providing a robust picture of spatiotemporal
distributions; and then ii) simulated an area closure based on areas defined
from the different data sources at a range of temporal and spatial resolutions.\\
%%
Our framework allows users to explore the assumptions in modelling
observational data and evaluate the underlying dynamics of such approaches at a
fine spatial and temporal scale. In application to a mixed fishery exploiting
four different populations we found different spatial patterns were evident and
that the effectiveness of the spatial closure reduced when data were aggregated
across larger spatial areas. However, aggregation across time periods has less
of a negative impact on the closure success and while not as effective as when
based on on the true population, closures based on high catch rates observed in
commercial data could still reduce fishing on a protected species. \\
